---
title: "Week 2 Breakouts"
author: "ITEC 621"
date: "7/9/2018"
output: html_document
---

Answer the following questions by writing R code. Add your code in the corresponding code blocks below and note that some -- but not all -- code is provided for certain questions. When you're done, try knitting your `.Rmd` into an `.html` document. 

# Breakout 1

Computing the length, or norm, of a vector x is similar to finding the hypotenuse of a triangle. 
To find the norm of x we do the following:

1. Square all entries in `x`.
2. Take the sum of `(1)`.
3. Take the square root of the sum in `(2)`.

## Question 1
Write a function `my_norm(x)` that computes the length of a vector x. Use your function to compute the norm of the vectors `(3, 4)` and `(5, 12)`.

**Bonus**: Can you write the function in one line?

```{r}
my_norm = function(x) {
  return(x)  
}

my_norm(c(3,4))
```


## Question 2
Write a function `max_norm(x, y)` that computes the norms of two vectors `x` and `y`, and returns only the greater value. (Hint: See `max()` )

```{r}
max_norm = function(x) {
  return(x)
}

max_norm(c(3,4))
```

## Question 3
Write a function `exclude_norm(x)` that computes the norm of a vector `x`, similar to Q1, except it ignores the first entry of `x`.

```{r}
exclude_norm = function(x) {
  return(x)
}

exclude_norm(c(3,4))
```

# Breakout 2

Simulate the system from Week 2 Slides (see slide 20, code copied below).

```{r}
# Load library
library(MASS)

# Generate some random data for predictor variables x1, x2
nsamples = 100
set.seed(1)
x1 = rnorm(nsamples, mean=1, sd=1)
x2 = rnorm(nsamples, mean=5, sd=5)
epsilon = rnorm(nsamples, mean=0, sd=0.3)
ones = matrix(1,nsamples,1)

# Use a pre-chosen formula to create dependent variable y
# (Ground truth)
X = cbind(ones, x1, x2)
X[1:3,]
b = c(1.6, 3, -2)
y = X %*% b + epsilon
```

## Question 1

Estimate a model `b_est` from the data `y` and `X` using the function `ginv()`. How close is `b_est` to the true model `b`?
```{r}

```

## Question 2

Try changing the properties of the predictor variables:

* Give `x1 mean=100, sd=10`.

* Give `x2 mean=-5, sd=20`.

What happens now when you run the functions from above?


## Question 3. 
Now estimate a model using `lm()`. Call the result `model_est`. How does it compare to `b_est`?

**Bonus**: Try using summary() on the resulting linear model model_est.
```{r}
df = data.frame(y=y, X=X)
# model.lm = lm( , data=df)
```

## Question 4. 
Re-run Q3 where `epsilon` has `sd=3`. What does this do to `b_est` or `summary(model_est)`?
```{r}

```

# Bonus

## ISLR, Exercise 2.9 

This exercise involves the `Auto` data set studied in the lab. Make sure that the missing values have been removed from the data.

```{r}
# Load ISLR library
# Remove missing data values
```

a: Which of the predictors are quantitative and which are qualitative?  
```{r}

```

b: What is the *range* of each quantiative predictor?
```{r}

```

c: What is the mean and standard deviation of each quantiative predictor?

**Hint**: Try using `describe()` in `library(psych)`.
```{r}

```

d: Now remove the 10th through 85th observations. What is the range, mean, and standard deviation of each quantiative predictor in the subset of data that remains?
```{r}

```

e: Using the full data set, investigate the predictors graphically using scatterplots or other tools of your choice. Comment on your findings.

**Hint**: Try using `ggpairs()` in `library(GGally)`.
```{r}

```

f: Suppose that we wish to predict gas mileage (`mpg`) on the basis of the other variables. Do your plots suggest that any of the other variables might be useful in predicting `mpg`? Justify your answer.
```{r}

```

