---
title: "W1 Lab"
author: "ITEC 621"
date: "10/4/2018"
output: html_document
---

**Important:** Before starting, make your own copy of this file with your initials at the end, e.g. `W1_Lab_gmf.Rmd`. This way your changes won't conflict with the class repo and are easier to track.

First, try clicking into the R console and typing the commands in the code block below, one by one.

```{r}
library(ISLR)
names(College)
class(College)
head(College)
summary(College)
head(College$Apps)
hist(College$S.F.Ratio, 30)
```

Next, try navigating to the line `library(ISLR)` from within the .Rmd editor in RStudio. Type `CTRL+Enter` and watch the line flash green (hopefully). Then navigate down each line and repeat, watching the output. Notice the same lines are being run in `Console`.

What does each function do?

Now try running the following lines:

```{r, eval=FALSE}
College.small = College[ , c('Apps', 'Accept')]
ggpairs(College.small)
```

You should receive an error (and a red flash in the text editor):

```
Error: could not find function "ggpairs"
```

Go to the console and type 
```{r}
??ggpairs
```

Notice there's a match: 

```
GGally::ggpairs
```

Which means the function is in a library called GGally. Let's load the library and try again:

```{r}
library(GGally)
College.small = College[ , c('Apps', 'Accept')]
ggpairs(College.small)
```

Additionally, let's comment out the offending line. Where we got an error with `ggpairs(College.small)`, let's add a `#` at the beginning of the line, which should cause it to change colors in the text editor.

# Bonus
```{r}

# Q1. The (Euclidean) length, or norm, of a vector x is computed by
# 1) Square all entries in x
# 2) Sum the squared entries from (1)
# 3) Take the square root of the sum from (2)
# Write a function my_norm(x) that computes the Euclidean length of a vector x. 
# Bonus: Can you write it in one line?
# Use your function to compute the norm of the vectors (3, 4) and (5, 12)

my_norm = function(x) {
  return(x)
}

my_norm(c(3,4))
my_norm(c(5,12))
```


```{r}
# Q2. Write a function max_norm(x, y) that computes the norm of x and y, and returns only the greater value. (Hint: See max() )

max_norm = function(x) {
  return(x)
}

max_norm(c(3,4))
max_norm(c(5,12))
```

```{r}
# Q3. Simulate the system from W1 Slide 10. Run the commented functions and describe the outputs.
# Change the parameters to the system from W1 Slide 10:
# Give x1 mean=100, sd=10.
# Give x2 mean = -5, sd=20. 
# What happens now when you run the functions from above?

# Generate some random data
nsamples = 100
set.seed(1)
x1 = rnorm(nsamples, mean=1, sd=1)
x2 = rnorm(nsamples, mean=5, sd=5)
epsilon = rnorm(nsamples, mean=0, sd=0.3)
ones = matrix(1,nsamples,1)

# Organize data
X = cbind(ones, x1, x2)
X[1:3,]
b = c(1.6, 3, -2)
y = X %*% b + epsilon

# Estimate model
library(MASS)
b_est = ginv(X) %*% y
b_est

```