---
title: "Week 2 Lab"
author: "ITEC 621"
date: "10/11/2018"
output: html_document
---

**Important:** Before starting, make your own copy of this file with your initials at the end, e.g. `W2_Lab_gmf.Rmd`. This way your changes won't conflict with the class repo and are easier to track.

Answer the following questions by writing R code. Add your code in the corresponding code blocks below and note that some -- but not all -- code is provided for certain questions. When you're done, try knitting your `.Rmd` into an `.html` document. 

### Q1: ISLR, Exercise 2.9 

This exercise involves the `Auto` data set from the ISLR textbook/library.

```{r}
# First we'll load the data and remove any rows with missing values
library(ISLR)
Auto = na.omit(Auto)
```

a: Which of the predictors are quantitative and which are qualitative?  
```{r}
# Add code here
```

Add any text for part a here.

b: What is the *range* of each quantiative predictor?
```{r}

```

c: What is the mean and standard deviation of each quantiative predictor?

**Hint**: Try using `describe()` in `library(psych)`.
```{r}

```

d: Now remove the 10th through 85th observations. What is the range, mean, and standard deviation of each quantiative predictor in the subset of data that remains?
```{r}

```

e: Using the full data set, investigate the predictors graphically using scatterplots or other tools of your choice. Comment on your findings.

**Hint**: Try using `ggpairs()` in `library(GGally)`.
```{r}

```

f: Suppose that we wish to predict gas mileage (`mpg`) on the basis of the other variables. Do your plots suggest that any of the other variables might be useful in predicting `mpg`? Justify your answer.
```{r}

```

### Q2

Computing the length, or norm, of a vector x is similar to finding the hypotenuse of a triangle. 
To find the norm of x we do the following:

* Square all entries in `x`.
* Sum the squared entries.
* Take the square root of the sum.

Write a function `my_norm(x)` that computes the length of a vector x. Use your function to compute the norm of the vectors `(3, 4)` and `(5, 12)`.

**Bonus**: Can you write the function in one line?

```{r}
my_norm = function(x) {
  # Add / replace code in here
  return(x)  
}

test_vec1 = c(3, 4)
test_vec2 = c(5, 12)

# This should output 5
my_norm(test_vec1)

# This should output 13
my_norm(test_vec2)
```


### Q3
Write a function `max_norm(x, y)` that computes the norms of two vectors `x` and `y`, and returns only the greater value. (Hint: See `max()` )

```{r, eval=FALSE}
max_norm = function(x) {
  # Add / replace code in here
  # Also, delete eval=FALSE from the header above
  return(x)
}

max_norm(test_vec1, test_vec2)
```

### Q4

Write a function `exclude_norm(x)` that computes the norm of a vector `x`, similar to Q1, except it ignores the first entry of `x`.

```{r}
exclude_norm = function(x) {
  return(x)
}

# This should output 4
exclude_norm(test_vec1)

# All of these should output 5:
exclude_norm(c(1, 3, 4))
exclude_norm(c(2, 3, 4))
exclude_norm(c(10, 3, 4))
```

### Q5: Simulation Study (Bonus)

Simulate the three-dimensional system below.

```{r}
# Load library
library(MASS)

# Generate some random data for predictor variables x1, x2
nsamples = 100
set.seed(1)
x1 = rnorm(nsamples, mean=1, sd=1)
x2 = rnorm(nsamples, mean=5, sd=5)
epsilon = rnorm(nsamples, mean=0, sd=0.3)
ones = matrix(1,nsamples,1)

# Use a pre-chosen formula to create dependent variable y
# In real world situations, this ground truth formula
# isn't known to us. But since this is simulation, we control it.
X = cbind(ones, x1, x2)
X[1:3,]
b = c(1.6, 3, -2)
y = X %*% b + epsilon
```

Estimate a model `b_est` from the data `y` and `X` using the function `ginv()`.
```{r, eval=FALSE}
# Remove eval=FALSE above and modify the code below
b_est = X %*% y
b_est
```

How close is `b_est` to the true model `b`?

Now try changing the properties of the predictor variables:

* Give `x1 mean=100, sd=10`.

```{r, eval=FALSE}
x1 = rnorm(nsamples, mean=1, sd=1)
X = cbind(ones, x1, x2)
y = X %*% b + epsilon
b_est = X %*% y
b_est
```

* Give `x2 mean=-5, sd=20`.

```{r, eval=FALSE}
x2 = rnorm(nsamples, mean=1, sd=1)
X = cbind(ones, x1, x2)
y = X %*% b + epsilon
b_est = X %*% y
b_est
```

What happens now to the estimated model `b_est` now?

Now estimate a model using `lm()`. Call the result `model_est`. How does it compare to `b_est`?

