---
title: "Week 4 Lab"
author: "ITEC 621"
date: "10/25/2018"
output: html_document
---

# Question 1
Consider the data frame `Hitters`.
```{r}
# First, load `Hitters` with `library(ISLR)`. 

# Then save a reduced data frame `Hitters.mod` which has the columns `Hits, Walks, HmRun, RBI, AtBat, Years, Salary`. Also, remove the rows with NA values with
# na.omit()


# Finally, use `ggpairs()` to plot the variables in `Hitters.mod`.
# Hint: Which library do we need?



```

# Question 2
```{r}
# Plot a histogram of `Hitters.mod$Walks` and comment on its features. 

# Next add three columns to the `Hitters.mod` data frame.
# For each one, plot a histogram.
# 2.1 `WalksCenter`, a centered version of `Hitters$Walks`

# 2.2 `WalksZ`, a standardized version of `Hitters$Walks`

# 2.3 (Bonus) `WalksPctile`, a percentile version of `Hitters$Walks`

```

# Question 3
```{r}
# Suppose you had 65 walks

# 3.1 Were you above/below the mean number of hits? 
# How many hits above/below the mean?

# 3.2 How many standard deviations above/below the mean did you have?

# 3.3 What would your percentile rank be within the `Hitters.mod` data frame? (Hint: Try `ecdf(Hitters.mod$Walks)()`)
ecdf(Hitters.mod$Walks)(65)
```


```{r}
# 4. Fit four models based on the formulas below. Print model summaries and compare the coefficients.
# 4.1 `Salary ~ Years + Hits + Walks`

# 4.2 `Salary ~ Years + Hits + WalksCenter`

# 4.3 `Salary ~ Years + Hits + WalksZ`

# 4.4 `Salary ~ Years + Hits + WalksPctile`


```

# Question 5
```{r}
# Using the values you computed in Q3 and the coefficients for `model`, `model.center`, and `model.z` from the summaries in Q4, predict the Salary for Barry Bonds, who had the following stats in 1986: `Years=1, Hits=92, Walks=65`. Then compare all three models using an ANOVA test, `anova()`.

# model:

# model.center:

# model.z:

# model.ptile:


# anova:

```

# Question 6
```{r}
# 6. Fit four models based on the formulas below. Print model summaries and compare the coefficients.

# Note we need this so we never take log(0)
Hitters.mod$Walks = Hitters.mod$Walks + 0.001

# 6.1 `Salary ~ Years + Hits + poly(Walks, 2)`


# 6.2 `Salary ~ Years + Hits + log(Walks)`


# 6.3 `log(Salary) ~ Years + Hits + Walks`


# 6.4 `log(Salary) ~ Years + Hits + log(Walks)`


```

7. Using the values you computed in Q3 and the coefficients for `model.poly`, `model.logx`, `model.logy`, and `model.loglog` from the summaries in Q6, predict the Salary for Barry Bonds, who had the following stats in 1986: `Years=1, Hits=92, Walks=65`. Note we *can't* use an ANOVA test on these models, since we transform Y in some cases. ANOVA requires identical Y across models.

```{r}
# model.poly:

# model.logx:

# model.logy:

# model.loglog:

```


